Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-03-07 Response/response-1.tex

\resp The proposed algorithm is a function of the number of backlogged packets and the channel conditions of all users in the network. Since the delay is proportional to the average number of backlogged packets in system, the proposed algorithm performs equally good in comparison with the existing Q-WSRM approach. It can be easily verified by the equivalence between the \me{\ell_2} norm JSFRA and the Q-WSRM scheme on page 4, col. 2, Section III-B starting paragraph. We have also provided the performance of different JSFRA algorithm and Q-WSRM scheme based on the average number of backlogged packets in the system over multiple transmission slots by varying the average number arrivals for all users in the system in Fig. 4 on page 13. We can still control the delay behavior by controlling the priority factor \me{a_k} in (6a), which affects the resource allocation. For example, if we consider a VOIP transmission, the delay requirements are stringent and it can be achieved by increasing the priority factor \me{a_k} in the current formulation. In addition, we can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem. We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.

\cmnt{3} \textit{In Section III.B, the convergence conditions under Algorithm 1 are not clear. First, you should be more specific about what is the SCA subproblem. Do you mean problem (19)? Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?}

\resp We understand the reviewer's point. We have updated the revised manuscript to discuss the convergence of the centralized algorithm in detail in Appendix B on page 14, col. 1. The discussions are provided for the convergence of the iterative algorithm. The uniqueness of the convex subproblem (20) can be guaranteed when the objective is non-zero for all coordinating BSs in the precoder design. It is due to the linear constraint on the transmit precoders in (19), which is susceptible to the transmit precoder phase rotations. On the other hand, the constraint in (16b) is not, since the precoder variable is inside the absolute value operator. Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16). The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D on page 15, col. 2.

@@

\cmnt{12} \textit{What is “SRA” in the simulation figures?}

\resp The \acf{SRA} is updated in the revised manuscript on page 7, col. 1, Section III-D.

\cmnt{13} \textit{In the discussion for Fig. 1, you mentioned that JSFRA converge to the optimal point, and all algorithms are Pareto-optimal. Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?}

\resp We thank the reviewer for pointing out the mistake in the text. Since the problem is nonconvex, the JSFRA formulation can find a local optimal point upon convergence. The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-E on page 15, col. 2. We have removed the statement mentioning the pareto-optimal solutions in the discussions on Fig. 1 in the revised manuscript.

### 2015-03-07 Report/convergence_centralized.tex
final_draft

\subsection{Boundedness of the Objective and Compactness of the Set}

@@

\subsection{Monotonicity}

@@

@@

\subsection{Convergence of the beamformer iterates}

Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and let \me{\mc{A}} be a point-to-set mapping from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}. The objective function \me{f} in \eqref{con-cvx} is continuous and the iterative algorithm yields monotonically decreasing objective values \me{f(\ma^{(n)}) \leq f(\ma^{(n-1)})} in each iteration. Therefore, the operator \me{\mc{A}} is monotonic with respect to a continuous objective function \me{f} yielding a sequence of beamforming iterates \me{\{\ma^{(n)}\}}. The following conditions are satisfied by the iterative algorithm \cite{meyer1976sufficient}.
\begin{itemize}

\end{itemize}

. Let \me{\{\ma^{(n)}\}} be the sequence of beamforming iterates generated by the function \me{f} in \eqref{con-cvx} and the mapping operator \me{\mc{A}}. To prove the convergence of the beamformer iterates, following conditions are required \cite{meyer1976sufficient}.
\begin{itemize}
\item[(e)] The mapping operator \
\end{itemize}

approaches a limiting or accumulation point \me{\ma^{\ast} \in \mc{F}^\ast} as \me{n \rightarrow \infty}, where \me{\mc{F}^{\ast}} represents the set of accumulation points for the

@@

To show the limiting point of the iterative algorithm is the stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem. As \me{i \rightarrow \infty} asymptotically, it satisfies
\allowdisplaybreaks{\begin{multline} \label{con-opt}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
\end{multline}}
where the solution point is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions. Using the above arguments, we can show that the \ac{JSFRA} schemes attains a stationary point of the original nonconvex problem.

>>>>

\subsection{Bounded Objective Function and Compact Feasible Set}

@@

\subsection{Monotonicity} \label{mcity}

@@

\subsection{Convergence of the Beamformer iterates}

Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{k+1} \in \mc{A}(\iterate{\ma}{k})}. The set of accumulation points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous. Let \me{\{\iterate{\ma}{k}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}. If the mapping is strictly monotonic and uniformly compact, then the following conditions hold \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}.
\begin{itemize}
\item[(i)] all accumulation points will be fixed points,
\item[(ii)] \eqn{f(\iterate{\ma}{k}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e} \eqn{\|\iterate{\ma}{k} - \iterate{\ma}{k+1} \| \rightarrow 0}.
\end{itemize}

The mapping \eqn{\mc{A}} for the iterative algorithm is given by
\begin{equation}
\mc{A}(\iterate{\ma}{k}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{k}), \; \text{subject to} \; \ma \in \mc{F},
\end{equation}
where \me{\iterate{\ma}{k} \in \mc{A}(\iterate{\ma}{k})}. The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{A}(\ma)}, as discussed in Appendix \ref{mcity}. The sequence of iterates \me{\{\iterate{\ma}{k}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}. The sequence \me{\{\iterate{\ma}{k}\}} converges to the set of fixed point \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.

To show the set of fixed points \me{\mc{F}^\ast} are the minimizer for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration. Since \me{f(\mc{A}(\iterate{\ma}{k}) < f({k})}, the objective decreases monotonically for each iteration and the equality achieves when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point. Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizer for the objective function \me{f} over the set \me{\mc{F}}.

If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{k+1} = \mc{A}(\iterate{\ma}{k})} and the accumulation point is unique. The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{meyer1976sufficient,zangwill1969nonlinear}. Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\ast} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.

@@

@@

To show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
\allowdisplaybreaks{\begin{multline} \label{con-opt}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
\end{multline}}
where the solution point is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions. Using the above arguments, we can show that the \ac{JSFRA} schemes attains a stationary point of the original nonconvex problem.
